Consistent Polyhedral Surrogates via Embedding

### 2019-05-22 notes/bo-separated.tex
notes from chat with raf about proof

The next lemma shows that if a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
\begin{lemma} \label{lemma:calibrated-pos}
  Let $\mathcal{U}' \subseteq \mathcal{U}$.
  If $\cap_{U\in\mathcal{U}'} U \neq \emptyset$ then $\cap_{U\in\mathcal{U}'} R_U \neq \emptyset$.
\end{lemma}
\begin{proof}
  \bo{already have this: it is our proof that a calibrated link is possible!}
\end{proof}

@@

>>>>

The next lemma shows that if a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
\begin{lemma} \label{lemma:calibrated-pos}
  Let $\mathcal{U}' \subseteq \mathcal{U}$.
  If $\cap_{U\in\mathcal{U}'} U \neq \emptyset$ then $\cap_{U\in\mathcal{U}'} R_U \neq \emptyset$.
\end{lemma}
\begin{proof}
  Let $u \in \cap_{U\in\mathcal{U}'} U$.
  Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
  Therefore, if we have $p$ such that $u$, then $r$ is optimal.
  Since $u \in U$, we have $r \in R_U$.
  This holds for all $U \in \mathcal{U}'$, so $r \in \cap_{U\in\mathcal{U}'} R_U$, so it is nonempty.
\end{proof}

@@

  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}
